%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Product Engineer} % Job title
    {Entri.me} % Organization
    {Ernakulam, Kerala} % Location
    {Feb. 2015 - Present} % Date(s)
    {\begin{cvparagraph} % Description(s) of tasks/responsibilities
       Entri, is Cochin based product startup that provide a Plug and Play learning system for teachers and students in India. 19,000 students, 400 teachers and 32 institutes have used Entri to improve their learning and teaching so far. Entri is the first company from India to get selected into LearnLaunch in Boston, USA.
\end{cvparagraph}
}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {One of the initial employees}
        \item {Designed a payment processing system and integrated with Payumoney and Razorpay for processing the payments}
        \item{Integrated with SendGrid for transactional emails and Mvaayoo for transactional sms}
        \item{Designed and implemented REST APIs to support entri.me Android Application}
        \item{Developed responsive web applications with Bootstrap and Sass preprocessor}
        \item{Created dashboard to track and analyse student performance for teachers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {software Trainee} % Job title
    {Recursive Labs} % Organization
    {Ernakulam, Kerala} % Location
    {March. 2014 - Jan. 2015} % Date(s)
    {\begin{cvparagraph} % Description(s) of tasks/responsibilities
       Mentorship program to become a better programmer by reading books, writing code, participating in Massive Open Online Courses(MOOC) and pursuing personal projects.
\end{cvparagraph}
}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used GNU/Linux Operating System from day 1 and did Python based projects and programming assignments.}
        \item {Gained exposure in developing web applications using Python based frameworks like Django and Flask}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
